Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2018-07-11 paper/galsize_paper.tex
Added KITP grant acknowledgement

Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357. This research was supported in part by the National Science Foundation under Grant No. NSF PHY11-25915.  AK was  supported by NSF grant  AST-1412107, and by the Kavli Institute for Cosmological Physics at the University of Chicago through grant PHY-1125897, and an endowment from the Kavli Foundation and its founder Fred Kavli. BPM acknowledges an Emmy Noether grant funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) -- MO 2979/1-1.

>>>>

Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357. This research was supported in part by the National Science Foundation under Grants No. NSF PHY11-25915. Research for this paper was initiated at the Kavli Institute of Theoretical Physics workshop on the Galaxy-Halo Connection, which is supported by NSF PHY17-48958. AK was supported by NSF grant  AST-1412107, and by the Kavli Institute for Cosmological Physics at the University of Chicago through grant PHY-1125897, and an endowment from the Kavli Foundation and its founder Fred Kavli. BPM acknowledges an Emmy Noether grant funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) -- MO 2979/1-1.
